---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  error = TRUE
)
```
# transx

<!-- badges: start -->
<!-- badges: end -->

The goal of transx is to ...

## Installation

You can install the released version of transx from [CRAN](https://CRAN.R-project.org) with:

``` r
remotes::install_github("transx")
```

## Motivation

### Problem

```{r problem, message=FALSE}
library(dplyr)

illu_data <- gapminder::gapminder %>% 
  filter(country == "Afghanistan") 

illu_data %>% 
  mutate(pop_lag = stats::lag(pop))

# dplyr has thought about this problem
illu_data%>% 
  mutate(pop_lag = dplyr::lag(pop))

```
However, this problem extends to all the univariate functions that are applied in
the same manner in a data.frame. For example

```{r example-diff}
illu_data %>% 
  mutate(pop_diff = base::diff(pop))
```

The idea for `transx` is coming from the need to construct wrapper functions.

```{r new-fun}
diffx <- function(x, ...) x - dplyr::lag(x, ... )

illu_data %>% 
    mutate(pop_diff = diffx(pop))
```

## Categories 

### Basic Trasformation

- [] leadx: Lead values
- [] lagx: Lag values

- [] diffx: Simple Differences
- [] ldiffx: Logarithic Differences
- [] rdiffx: Percentage change

- [] standarise
- [] normalise
- [] normalise0
- [] minmax
- [] demean

## Power Transform

- [] boc_cox: Box-Cox
- [] yeo_johnsonYeo-Johnson

## Trend

### Deterministic Trend

- [] dtrend_lin():
- [] dtrend_quad():
- [] dtrend_poly():

### Stochastic Trend

- [] st_arima

### Cycle Trend Decomposition

filter_*

- [] filter_hp(): Hodrick Prescot
- [] filter_bk(): Baxter King
- [] filter_cf(): Chirstiano Fitzgerlard
- [] filter_bw(): Buttersword
- [] filter_tr(): Trigonometric
- [] decomp_bn(): Beveridge-Nelson decomposition

- [] filter_ham: Hamilton

## Outliers

out_*

- [] out_drop()
- [] out_trim()
- [] out_trim_qt()
- [] out_winsorize()

## Smoothers

sm_*

2. Local smoothers

- [] smooth_holt_winters: Holt Winters - https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/HoltWinters
- [] smooth_exp(): Expontential Smoothin
- [] smooth_ma(): 
- [] smooth_mm():
- [] smooth_gaussian:
- [] smooth_wiener:
- [] smooth_kalman() :
- [] smooth_nn: Nearest neighbor smoother
- [] smooth_kernel(): Kernel smoothers
- [] smooth_spline(): Smoothing splines
<!-- - [] sm_loess(): LOESS (locally estimated scatterplot smoother)  -->

## Resampling

- [] resample():
- [] resample_norm():
- [] resample_rad():
- [] resample_mammen():

## Window Operations

### Recursive

rec_*

- [] rec_fun
- [] rec_sample
- [] rec_sum
- [] rec_mean
- [] rec_median
- [] rec_prod
- [] rec_var
- [] rec_sd
<!-- - [] rec_qt
- [] rec_skew
- [] rec_kurt -->
- [] rec_max
- [] rec_min

### Rolling

roll_*

- [] roll_fun
- [] roll_sample
- [] roll_sum
- [] roll_mean
- [] roll_median
- [] roll_prod
- [] roll_var
- [] roll_sd
- [] roll_max
- [] roll_min

### Block 

blck_*

- [] blck_fun
- [] blck_sample
- [] blck_sum
- [] blck_mean
- [] blck_median
- [] blck_prod
- [] blck_var
- [] blck_sd
- [] blck_max
- [] blck_min
