---
title: "motivation"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{motivation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(transx)
```

Some functions require inheritnly the frequency (like decompose or stl) of the time-series. Although the input can be `ts` and `xts` object, the output will always be a numeric vector.

### Problem

* stats
* dplyr
* tsibble

We restrict tibble printing options to minimize the space occupied.

```{r problem, message=FALSE}
library(dplyr)
options(tibble.print_min = 3)
```

Let's load the economics dataset from `ggplot2` for illustration.

```{r}
econ <- ggplot2::economics
econ
```

Then, we are going to use some `stats` functions:

```{r exist-already}
econ %>% 
  mutate(pop_lag = stats::lag(pop))
```

`base::lag` only works on `ts` objects. However, dplyr has thought about this problem

```{r dplyr-lag}
econ %>% 
  mutate(pop_lag = dplyr::lag(pop))
```


However, this problem extends to all the univariate functions that are applied in
the same manner in a data.frame. For example

```{r example-diff, error=TRUE}
econ %>% 
  mutate(pop_diff = base::diff(pop))
```

The idea for `transx` is coming from the need to construct wrapper functions.

```{r new-fun}
diffx <- function(x, ...) x - dplyr::lag(x, ... )

econ %>% 
    mutate(pop_diff = diffx(pop))
```
